Slavnov products and KP tau functions

### 2025-04-08 draft.tex
add tau function in terms of Miwa coordinates

\subsection{Tau functions}

@@

In fact, we can focus all our attention on a particular function. Therefore,
for a fixed \(\ell\), we define the vector \( \bm{z} \equiv \bm{u}_\ell\).
Consequently, 
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Delta(\bm{z})} \det[\Omega_j(z_k) ]_{j,k=1}^n \\
  & = \frac{1}{\Delta(\bm{z})} \det\left[\frac{\mathcal{Y}_j(z_k)}{z_k - v_j} \right]_{j,k=1}^n  \\
\end{split}
\end{equation}
All these tau functions have the form of an
\emph{alternant determinant} \footnote{see definition~(\ref{def:alt-determinant})
in the appendix~\ref{app:mathematical}.}

@@

Finally, let we write \(z_1 \equiv w\) and using elementary row operations we find
\begin{equation}
  \bm{\tau}_h(w, \bm{v}) =
  \frac{1}{\prod_{k=1}^n(w - v_k)}
  \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \dots, \mathcal{Y}_n](w)
  \; .
\end{equation}
that agrees with the results we obtained above.

\end{subequations}

@@

It seems that we can consider a basis of functions \(\mathcal{Y}_j(z)\) for the Baker-Akhiezer
functions. I think that this object might say something interesting. In particular, we can
explicitly build solutions of the KP equation. In fact, the functions \(\mathcal{Y}_j\)
above have poles at the Bethe roots, it is interesting. 
\begin{itemize}
\item[\faCheck] What is the pole and root structure of the tau and Baker-Akhiezer (BA) functions?
  In particular, what happens at the Bethe roots?
\item[\faCheck] Basis tau functions
\item[\faCheck] Write the cases n=2 and n=3
\item[\faCheck] What the general case for all \(z_k\) approaching to a single
  value \(w\). 
\item Write these tau functions in terms of Miwa coordinates
\item It turns out that the Baker-Akhiezer function is the appropriate object to discuss
  the Bethe roots. 
  \item I think that these tau functions come from algebro geometric tau functions. 
  \item I can try to study the dynamics closer to the Bethe roots, I think that the
    \(\Omega\)'s will have some interesting expansions, some of them might vanish. 
  \item This might become a Riemann Hilbert problem
  \item Are these tau functions associated to the Calogero-Moser model??
  \item Elliptic case - see slavnov, zabrodin's paper
\end{itemize}

>>>>

\section{Tau functions}

@@

In fact, we can focus all our attention on a particular function. Therefore,
for a fixed \(\ell\), we define the vector \( \bm{z} \equiv \bm{u}_\ell\).
Consequently, 
\begin{equation}
\begin{split}
\label{eq:tau-function}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Delta(\bm{z})} \det[\Omega_j(z_k) ]_{j,k=1}^n \\
  & = \frac{1}{\Delta(\bm{z})} \det\left[\frac{\mathcal{Y}_j(z_k)}{z_k - v_j} \right]_{j,k=1}^n  \\
\end{split}
\end{equation}
All these tau functions have the form of an
\emph{alternant determinant}.

@@

Finally, let we write \(z_1 \equiv w\) and using elementary row operations we find
\begin{equation}
  \bm{\tau}_h(w, \bm{v}) =
  \frac{1}{\prod_{k=1}^n(w - v_k)}
  \mathcal{W}[\mathcal{Y}_1, \mathcal{Y}_2, \dots, \mathcal{Y}_n](w)
  \; .
\end{equation}
that agrees with the results we obtained above. 
\end{subequations}

\section{Miwa coordinates}

We now want to write the Slavnov products we defined above in terms of the following 
coordinates
\begin{equation}
  t_p = \frac{1}{p}\sum_{j=1}^n z_j^p\; ,
\end{equation}
the so called, Miwa coordinates.

We can show, see~\cite{Araujo:2021ghu} for a detailed proof of this
statement, that the tau function~\ref{eq:tau-function} admits an
integral representation of the form (ignoring the signs dependence on
the length \(n\) of the spin chain)
\begin{equation}
  \label{eq:tau-function-miwa}
  \bm{\tau}(\bm{t}, \bm{v}) = 
    \det_{j,k}\left(
    \oint \frac{d w}{2\pi i} e^{\bm{\xi}(\bm{t}, w^{-1})} \frac{w^{-j}\mathcal{Y}_k(w)}{w - v_k} \; ,
    \right)
\end{equation}
where 
\begin{equation}
  \bm{\xi}(\bm{t}, w^{-1}) = \sum_{p=1}^\infty t_p w^{-p}\; .
\end{equation}
One of the advantages of this representation is that now it makes
sense to consider the limit of the infinite chain, \(n\to \infty\).

@@

It seems that we can consider a basis of functions \(\mathcal{Y}_j(z)\) for the Baker-Akhiezer
functions. I think that this object might say something interesting. In particular, we can
explicitly build solutions of the KP equation. In fact, the functions \(\mathcal{Y}_j\)
above have poles at the Bethe roots, it is interesting. 
\begin{itemize}
\item[\faCheck] What is the pole and root structure of the tau and Baker-Akhiezer (BA) functions?
  In particular, what happens at the Bethe roots?
\item[\faCheck] Basis tau functions
\item[\faCheck] Write the cases n=2 and n=3
\item[\faCheck] What the general case for all \(z_k\) approaching to a single
  value \(w\). 
\item[\faCheck] Write these tau functions in terms of Miwa coordinates
\item It turns out that the Baker-Akhiezer function is the appropriate object to discuss
  the Bethe roots. 
  \item I think that these tau functions come from algebro geometric tau functions. 
  \item I can try to study the dynamics closer to the Bethe roots, I think that the
    \(\Omega\)'s will have some interesting expansions, some of them might vanish. 
  \item This might become a Riemann Hilbert problem
  \item Are these tau functions associated to the Calogero-Moser model??
  \item Elliptic case - see slavnov, zabrodin's paper
\end{itemize}
